Market Expectations and Mangerial Turnover

### 2024-03-12 paper.qmd
Update paper.qmd

```{r}
#| include: false
rm(list = ls())
library(brms)
library(tidyverse)
library(rstan)
library (tidybayes)
reticulate::use_condaenv("pymc")

@@

```{r}
#|label: tbl-managertype
#| tbl-cap: "Manager types"
library(kableExtra)
terms_to_remove <- c("1.FC Köln II","Al-Ahli (UAE)","Gimnasia (J)","San Martín (T)",
  "San Martín (SJ)","Racing (Cba)","Juv. Unida (G)","1.FC Köln U19",
  "1.FC Köln U17","1.FC Köln Yth.",
  "1.FC Köln U16"," II","1.FC Köln","Bor. M'gladbach",
  "Hertha BSC","F. Düsseldorf",
  "Velez Mostar","SSV Reutlingen","FV Ravensburg",
  "Fenerbahce","FC Teningen","FV Nimburg","Heart of Midl.",
  "Vetra","Sp.Genzano (PZ)","Honvéd FC","Olympiacos","Honvéd SE","Hungary",
  "ADO Den Haag(A)","Dordrecht'90","Haarlem","AZ Alkmaar","Roda JC","AZ '67",
  "Sparta R.","De Treffers","NEC Nijmegen","FC Oss","VV Gemert","PSV U21")
spells %>%
  mutate(position = str_remove_all(position, paste0("(", paste(terms_to_remove, collapse = "|"), ")"))) -> spells
spells |> mutate(
    staff_position = trimws(tolower(position)),
    staff_position = ifelse(staff_position=="manager","manager",staff_position),
    staff_position = ifelse(staff_position=="assistant manager","assistant manager",staff_position),
    staff_position = ifelse(staff_position=="caretaker manager","caretaker manager",staff_position),
    staff_position = ifelse(str_detect(staff_position,"player-coach"),"player-coach",staff_position),
    staff_position = ifelse(str_detect(staff_position,"director of football"),"director of football",staff_position),
    staff_position = ifelse(str_detect(staff_position,"technical director"),"technical director",staff_position),
    staff_position = ifelse(str_detect(staff_position,"director of professional football"),"director of professional football",staff_position),
    staff_position = ifelse(str_detect(staff_position,"sporting director"),"sporting director",staff_position),
    staff_position = ifelse(str_detect(staff_position,"academy manager"),"academy manager",staff_position),
    staff_position = ifelse(str_detect(staff_position,"advisor"),"advisor",staff_position),
    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position),
    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position)) %>%
  {table(.$staff_position[!is.na(.$staff_position)])} |> sort(decreasing = TRUE) |> 
  # make the frequency table into a data frame
  as.data.frame() |>
  # rename the columns
  rename("staff_position" = "Var1", "n" = "Freq") |>
  # order the data frame by the frequency
  arrange(desc(n)) |>
  head(20) |>
  kable(col.names=c("Staff Role","Number")) |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
```

```{r}
#| label: fig-annual-spell-count
#| fig-cap: "Annual count of manager spell ending"
library(ggplot2)
library(dplyr)
# create plot of annual count of spells using a count of finishes per season assume season starts in August
spells |> mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |> 
  count(season_start) |> 
  ggplot(aes(x = season_start, y = n)) +
  geom_col(width = 0.5) +
  labs(title = "Annual count of spell ending", x = "Season", y = "Number of spells") +
  theme_minimal() -> spell_count
plotly::ggplotly(spell_count)
```

```{r}
```

>>>>

```{r}
#| include: false
rm(list = ls())
library(brms)
library(tidyverse)
library(rstan)
library (tidybayes)
#reticulate::use_condaenv("pymc")

@@

```{r}
#|label: tbl-managertype
#| tbl-cap: "Manager types"
library(kableExtra)
terms_to_remove <- c("1.FC Köln II","Al-Ahli (UAE)","Gimnasia (J)","San Martín (T)",
  "San Martín (SJ)","Racing (Cba)","Juv. Unida (G)","1.FC Köln U19",
  "1.FC Köln U17","1.FC Köln Yth.",
  "1.FC Köln U16"," II","1.FC Köln","Bor. M'gladbach",
  "Hertha BSC","F. Düsseldorf",
  "Velez Mostar","SSV Reutlingen","FV Ravensburg",
  "Fenerbahce","FC Teningen","FV Nimburg","Heart of Midl.",
  "Vetra","Sp.Genzano (PZ)","Honvéd FC","Olympiacos","Honvéd SE","Hungary",
  "ADO Den Haag(A)","Dordrecht'90","Haarlem","AZ Alkmaar","Roda JC","AZ '67",
  "Sparta R.","De Treffers","NEC Nijmegen","FC Oss","VV Gemert","PSV U21")
spells %>%
  mutate(position = str_remove_all(position, paste0("(", paste(terms_to_remove, collapse = "|"), ")"))) -> spells
spells |> mutate(
    staff_position = trimws(tolower(position)),
    staff_position = ifelse(staff_position=="manager","manager",staff_position),
    staff_position = ifelse(staff_position=="assistant manager","assistant manager",staff_position),
    staff_position = ifelse(staff_position=="caretaker manager","caretaker manager",staff_position),
    staff_position = ifelse(str_detect(staff_position,"player-coach"),"player-coach",staff_position),
    staff_position = ifelse(str_detect(staff_position,"director of football"),"director of football",staff_position),
    staff_position = ifelse(str_detect(staff_position,"technical director"),"technical director",staff_position),
    staff_position = ifelse(str_detect(staff_position,"director of professional football"),"director of professional football",staff_position),
    staff_position = ifelse(str_detect(staff_position,"sporting director"),"sporting director",staff_position),
    staff_position = ifelse(str_detect(staff_position,"academy manager"),"academy manager",staff_position),
    staff_position = ifelse(str_detect(staff_position,"advisor"),"advisor",staff_position),
    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position),
    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position)) -> spells

spells %>%
  {table(.$staff_position[!is.na(.$staff_position)])} |> sort(decreasing = TRUE) |> 
  # make the frequency table into a data frame
  as.data.frame() |>
  # rename the columns
  rename("staff_position" = "Var1", "n" = "Freq") |>
  # order the data frame by the frequency
  arrange(desc(n)) |>
  head(20) |>
  kable(col.names=c("Staff Role","Number")) |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
```

```{r}
#| label: fig-annual-spell-count
#| fig-cap: "Annual count of manager spell ending"
library(ggplot2)
library(dplyr)
# create plot of annual count of spells using a count of finishes per season assume season starts in August
spells |> 
  mutate(youth_team = ifelse(str_detect(club, "[A-Z][0-9]{2}|Yth."), "Yes", "No")) -> spells

# Create a list of the worlds countries in lowercase
countries <- c("albania", "andorra", "austria", "belarus", "belgium", "bosnia-herzegovina", "bulgaria", "croatia", "cyprus", "czech-republic", "denmark", "estonia", "faroe-islands", "finland", "france", "germany", "gibraltar", "greece", "hungary", "iceland", "ireland", "italy", "kosovo", "latvia", "liechtenstein", "lithuania", "luxembourg", "malta", "moldova", "montenegro", "netherlands", "north-macedonia", "northern-ireland", "norway", "poland", "portugal", "romania", "russia", "san-marino", "scotland", "serbia", "slovakia", "slovenia", "spain", "sweden", "switzerland", "turkey", "ukraine", "wales", "england")

# find the name of a country in the club name
spells |> 
  mutate(country = str_extract(club, "([A-Z][a-z]+)")) |> 
  filter(!is.na(country)) |> 
  count(country) |> 
  arrange(desc(n)) |> 
  head(20) |> 
  kable(col.names=c("Country","Number")) |> 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)

# plot the annual count of spells using a count of finishes per season assume season starts in August and condition on youth_team
spells |> 
  filter(staff_position=="manager") |> 
  mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |>
  group_by(season_start,youth_team) |>
  count(season_start)

|> 
  ggplot(aes(x = season_start, y = n)) +
  geom_col(width = 0.5) +
  labs(title = "", x = "Season", y = "Number of spells") +
  theme_minimal() -> spell_count

plotly::ggplotly(spell_count)
```
